\textbf{quicR}:\ An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays

### 2025-03-13 man/manuscript/softwareX_submission.tex
Finally fixed .gitignore. Had to add "*" in front of file extensions.
Updated the keywords

        \begin{keyword}
            R package \sep{} RT-QuIC \sep{} prion \sep{} diagnostics \sep{} CJD \sep{} Parkinson's
        \end{keyword}

@@

    \begin{table}[ht]
        \fontsize{9pt}{9pt}\selectfont
        \centering
        \begin{tabular}{lp{6cm}p{6cm}}
            \hline{}
            \textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
            \hline{}
            C1 & Current code version & V2.1.0 \\
            % \hline{}
            C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0} \\
            % \hline{}
            C3  & Permanent link to Reproducible Capsule & \url{https://cran.r-project.org/web/packages/quicR}\\
            % \hline{}
            C4 & Legal Code License & GPL-3 \\
            % \hline{}
            C5 & Code versioning system used & Git \\
            % \hline{}
            C6 & Software code languages, tools, and services used & R \\
            % \hline{}
            C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0) \\
            % \hline{}
            C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
            % \hline{}
            C9 & Support email for questions & rowde002@umn.edu\\
            \hline{}
        \end{tabular}
    \end{table}

>>>>

        \begin{keyword}
            R package \sep{} RT-QuIC \sep{} Nano-QuIC \sep{} Micro-QuIC \sep{} prion \sep{} diagnostics \sep{} Creutzfeldt-Jakob \sep{} Chronic Wasting Disease \sep{} Parkinson's
        \end{keyword}

@@

    \begin{table}[ht]
        \fontsize{9pt}{9pt}\selectfont
        \centering
        \begin{tabular}{lp{6cm}p{6cm}}
            \hline{}
            \textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
            \hline{}
            C1 & Current code version & V2.1.0 \\
            % \hline{}
            C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0} \\
            % \hline{}
            C3  & Permanent link to Reproducible Capsule & \url{https://cran.r-project.org/web/packages/quicR}\\
            % \hline{}
            C4 & Legal Code License & GPL-3\\
            % \hline{}
            C5 & Code versioning system used & Git\\
            % \hline{}
            C6 & Software code languages, tools, and services used & R\\
            % \hline{}
            C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0)\\
            % \hline{}
            C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
            % \hline{}
            C9 & Support email for questions & rowde002@umn.edu\\
            \hline{}
        \end{tabular}
    \end{table}
